pathway coverage

### 2019-11-27 scripts/24_pathcoverage.Rmd
path coverage heatmap

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
library(tidyverse)
library(kableExtra)
```

@@

pwc %>% 
  filter(pwid %in% sig$pwid) %>% 
  select(-pwid) %>% 
  kable(caption = 'Look at the table of pathway coverage in each sample') %>% 
  kable_styling()
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
library(tidyverse)
library(kableExtra)
library(pheatmap)
```

@@

pwc %>% 
  filter(pwid %in% sig$pwid) %>% 
  select(-pwid) %>% 
  kable(caption = 'Look at the table of pathway coverage in each sample') %>% 
  kable_styling()

pwc_wide <-   pwc %>% 
  filter(pwid %in% sig$pwid) %>% 
  select(-pwid) %>% 
  column_to_rownames('pw')
```

@@

```{r}
# try to do a heatmap to see if there is some sample that is interesting to look at 
pheatmap(
  pwc_wide,
  #color=bwrPalette, 
  #annotation_col = annot,
  show_rownames = T,
  show_colnames = TRUE,
  filename = '../figs/pcov_hm.jpg',
  height = 10,
  width = 20,
  cluster_rows =T,
  cluster_cols=T
)
```
